{ \fontfamily{ptm}\selectfont A Title Here: A Sub Title Here }

### 2024-11-05 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, updated contents

\title{{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}}

@@

\begin{abstract} 
    \noindent
    Nesterov accelreated gradient method has been in the spotlight for the past decades due its wide spread applications and theories of optimal convergence. 
    Decades later it still opens up new interpretations. 
    Our work suggests a proximal point interpretation of accelerated gradient method for the method of accelerated proximal gradient method as a major extension to the interpretation proposed by Ahn and Sra \cite{ahn_understanding_2022}. 
    The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the proximal point interpreation. 
    Additionally, we conduct numerical experiment for a line search method that dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in for algorithm  using the proximal point understanding of accelerated gradient.

@@

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method (PPM) applied to an upper surrogate function, and then a lower surrogate function. 
    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations. 
    As a major extension, our work describes the method of proximal gradient using the PPM interpretations. We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof. We derive major variants of the Nesterov acceleation algorithm
    \cite{chambolle_convergence_2015}, \cite{beck_fast_2009-1}, \cite[Chapter 12]{ryu_large-scale_2022}
    of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form.

    \par
    Some of the earlier examples for the extension of the Nesterov acceleration method make use of the classical analysis introduced by Nestrov. 
    It uses the Nesterov acceleration sequence. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof. 
    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope for the Lypunov analysis.
    The interpration allows choices of undetermined parameters to encompass several variants of the Nesterov accelerated gradient algorithm. 
    Ahn and Sra's approach is inspired by works from Defazio \cite{defazio_curved_2019}, Zeyuan and Lorenzo \cite{allen-zhu_linear_2016}. 
    Instead of a mirror descent step on the dual, they propose an alternative without the gradient of the dual. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$ using Bregman Divergence. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge (weakly in Hilbert space), see Chambolle and Dossal \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator of a maximally monotone opreator in general is outside of the scope since it not all maximal monotone operator corresponds to a subgradient operator. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm leads to the valuable insight that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function. 
    In work by \cite{allen-zhu_linear_2016}, they interpreted the idea of Nesterov acceleration as a combinations of gradient descent and mirror descent.

    % \par
    % The paper is organized as follow: 
    % \begin{enumerate}
    %     \item Section 
    % \end{enumerate}

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
    \hyperref[assumption:smooth-nonsmooth-sum]
    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
    A lower bound function is identified using the gradient mapping operator and proved in
    \hyperref[lemma:grad_map_linearization]{Lemma \ref*{lemma:grad_map_linearization}}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth with constant $L$. 
    \end{assumption}
    \begin{definition}[Strongly convex functions]
        A function $f: X \mapsto \RR$ is $\beta$-strongly convex
        with $\beta\geq 0$ if $f - \beta \frac{\Vert \cdot\Vert^2}{2}$ is convex.
    \end{definition}

    \begin{theorem}[Proximal descent inequality]\label{thm:ppm_descent_ineq}
        Let $f: \RR^n \mapsto \overline \RR$ be $\beta$ strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
        For all $y \in \RR$ it verifies
        $$
            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
            - 
            \left(
                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
            \right)
            \le 
            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
        $$
        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
    \end{theorem}
    \begin{proof}
        See 
        \hyperref[appendix:proof_ppm_descent_lemma]
            {Appendix \ref*{appendix:proof_ppm_descent_lemma}}. 
    \end{proof}
    \begin{remark}
        We use this theorem to prove the convergence of the proximal point method. 
        Observe that when $\beta = 0$, this reduces to \cite[theorem 12.26]{bauschke_convex_2017}. 
    \end{remark}

    \begin{definition}[The gradient mapping]
        \label{def:gradient_mapping}
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
        Define the proximal gradient operator
        $$
            \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
        $$
        and the gradient mapping operator
        $$
            \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
        $$
    \end{definition}
    \begin{remark}
        The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing. 
        Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
    \end{remark}

    \begin{lemma}[Gradient mapping approximates subgradient]
    \label{lemma:grad-map-approx-subgrad}\; \\
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref{assumption:smooth-nonsmooth-sum}}, 
        let $\mathcal T_L, \mathcal G_L$ be given by 
        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}.
        Then for all $x$, the gradient mapping verifies
        \begin{align*}
            x^+ &= \mathcal T_L(x), 
            \\
            \mathcal G_L(x) := L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
        \end{align*}
        Equivalently, $\exists v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + v = L(x - x^+)$. 
    \end{lemma}
    \begin{proof}
        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
        \begin{align*}
            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
            \\
            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
            \\
            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
            \\
            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
            \\
            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
            \\
            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
            \\
            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{proof}

    \begin{lemma}[Linearized gradient mapping lower bound]
    \label{lemma:grad_map_linearization}\; \\
        Suppose that $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        further assume that $f$ is strongly convex with index $\mu \ge 0$. 
        Let $x^+ = \mathcal T_L(x)$ as given in 
        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
        Then for all $z \in \RR$, it satisfies
        \begin{align*}
            h(z) &\ge 
            h(x^+) + 
            \langle \mathcal G_L (x), z - x\rangle 
            + 
            \frac{L}{2}\Vert x - x^+\Vert^2 + \frac{\mu}{2}
            \Vert z - x\Vert^2. 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Using the $L$-smoothness of $f$ and convexity of $g, f$, it has inequalities
        \begin{align*}
            &f(x^+) \le 
            f(x) + \langle \nabla f(x), x^+ - x\rangle
            + \frac{L}{2}\Vert x - x^+\Vert^2, 
            \\
            &
            \frac{\mu}{2}\Vert z - x\Vert^2+ 
            f(x) + \langle \nabla f(x), z - x\rangle 
            \le f(z), 
            \\
            &g(x^+) \le 
            g(z) + \langle v, x^+ - z\rangle\quad 
            \forall v \in \partial g(x^+)
        \end{align*}
        For all $v \in \partial g (x^+)$, apply the above by considering the following sequence of relations
        \begin{align*}
            h(x^+) &= f(x^+) + g(x^+)
            \\&
            \begin{aligned}
                &\le 
                \left(
                    f(x) + \langle \nabla f(x), x^+ - x\rangle
                    + \frac{L}{2}\Vert x - x^+\Vert^2
                \right)
                \\
                &\qquad  
                + (g(z) + \langle v, x^+ - z\rangle)
            \end{aligned}
            \\&
            \begin{aligned}
                &\le 
                \left(
                    f(z) - \langle \nabla f(x), z - x\rangle
                    - \frac{\mu}{2}\Vert z - x\Vert^2
                    + \langle \nabla f(x), x^+ - x\rangle
                    + 
                    \frac{L}{2}\Vert x - x^+\Vert^2
                \right)
                \\
                &\qquad 
                +
                (g(z) + \langle v, x^+ - z\rangle)
            \end{aligned}
            \\&
            \begin{aligned}
                &= 
                (f(z) + h(z)) 
                \\
                &\qquad 
                + \left(
                    \langle \nabla f(x), x - z\rangle + 
                    \langle \nabla f(x), x^+ - x\rangle + 
                    \langle v, x^+ - z\rangle
                \right) 
                \\ 
                &\qquad 
                - \frac{\mu}{2}\Vert z - x\Vert^2
                + \frac{L}{2}\Vert x - x^+\Vert^2
            \end{aligned}
            \\& 
            \begin{aligned}
                &= h(z) + 
                \left(
                    \langle \nabla f(x), x - x^+ + x^+ - z\rangle + 
                    \langle \nabla f(x), x^+ - x\rangle + 
                    \langle v, x^+ - z\rangle
                \right)
                \\
                &\qquad 
                - \frac{\mu}{2}\Vert z - x\Vert^2
                + \frac{L}{2}\Vert x - x^+\Vert^2
            \end{aligned}
            \\& 
            \begin{aligned}
                &= h(z) + 
                \langle \nabla f(x) + v, x^+ - z\rangle 
                - \frac{\mu}{2}\Vert z - x\Vert^2
                + \frac{L}{2}\Vert x - x^+\Vert^2
            \end{aligned}
        \end{align*}
        Showed in  
        \hyperref[lemma:grad-map-approx-subgrad]{Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + v = L(x - x^+)$, so it yields
        \begin{align*}
            h(x^+) & 
            \le  
            h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
            - \frac{\mu}{2}\Vert z - x\Vert^2
            + \frac{L}{2}\Vert x - x^+\Vert^2
            \\
            &= h(z) + 
            \underbrace{\langle L(x - x^+), x - z\rangle}_{
                = - \langle \mathcal G_L (x), z - x\rangle
            }
            - \frac{\mu}{2}\Vert z - x\Vert^2
            - \frac{L}{2}\Vert x - x^+\Vert^2
        \end{align*}
        Moving everything except $h(z)$ from the RHS to the LHS yield the desired inequality. 
    \end{proof}
    \begin{remark}
        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}, however Nesterov stated it only for the case when $g$ is an indicator function of some convex set $Q$. 
    \end{remark}

\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
    In this section, we present the generic PPM formulation of the accelerated proximal gradient method. 
    This is general form presents us with a set of undetermine stepsize parameters $\eta_i, \tilde \eta_i$ that can be changed later to accomodate proofs that take Lypunov functions and phrase the convergence rate using the stepsizes sequence $\tilde \eta_i$. 
    These interpretations are extension in the non-smooth context of Ahn and Sra's work \cite{ahn_understanding_2022} using the proximal gradient mapping operator. 
    The next definition will start the discussion. 
    \begin{definition}[Linear lower bounding function]\label{def:gradmap-linear-lowerbnd-fxn}
        Let $h = f+ g$ satisfies
        \hyperref[assumption:smooth-nonsmooth-sum]{Definition \ref*{assumption:smooth-nonsmooth-sum}}, 
        $\mathcal G_L$ given by 
        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
        Define for all $y$ the function
        \begin{align*}
            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
        \end{align*}
    \end{definition} 
    \begin{remark}
        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
        \hyperref[lemma:grad_map_linearization]
        {Lemma \ref*{lemma:grad_map_linearization}}. 
    \end{remark}
    \par
    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
    \par
    We state the PPM interpretation of accelerated gradient in 
    \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}, 
    which has the equivalent form as presented in
    \hyperref[def:ag_prox_grad_generic]
    {Definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[prop:derive_ag_prox_grad_tript]
    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
    shows their equivalence. 
    \par
    Through out this section, we assume 
    \begin{enumerate}
        \item $h=f + g$ satisfies 
            \hyperref[assumption:smooth-nonsmooth-sum]
            {Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
            \hyperref[def:gradient_mapping]
            {Definition \ref*{def:gradient_mapping}}. 
        \item Using all above, let $l_h$ be given by 
            \hyperref[def:gradmap-linear-lowerbnd-fxn]
            {Definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
    \end{enumerate}

    \begin{definition}[AG proximal gradient PPM generic form]
    \label{def:ag_prox_grad_ppm}
        Define $\eta_t, \tilde \eta_t$ to be strictly larger than zero for all $t \in \N$. 
        With initial iterate $x_0, y_0$, 
        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
        $$
        \begin{aligned}
            x_{t + 1} &= \argmin_{x} \left\lbrace
                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                \Vert x - x_t\Vert^2
            \right\rbrace,
            \\
            y_{t + 1}&= 
            \argmin_{x}
            \left\lbrace
                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
            \right\rbrace.
        \end{aligned}
        $$
    \end{definition}

    \begin{definition}[AG proximal gradient generic form]
    \label{def:ag_prox_grad_generic}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$.
        The generic form has iterates $(y_t, x_{t + 1}, z_{t + 1})$ such that 
        $$
        \begin{aligned}
            y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
            \\
            x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
            \\
            z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
        \end{aligned}
        $$
        for all $t\in \mathbb N$. 
    \end{definition}
    \begin{remark}
        Observe that $z_{t + 1} = y_t^+$. 
    \end{remark}

    \begin{proposition}
    \label{prop:derive_ag_prox_grad_tript}
       We have equalities
        \begin{align*}
            x_{t + 1} &= \argmin_{x}
            \left\lbrace
                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
            \right\rbrace
            \\
            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
            \\
            y_{t + 1} &= \argmin_{x}
            \left\lbrace
                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &= (1 + L\eta_{t + 1})^{-1}
            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
        \end{align*}
        This thows
        \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
        and 
        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}} 
        are equivalent. 
    \end{proposition}
    \begin{proof}
        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
        \hyperref[lemma:grad_map_linearization]
        {Lemma \ref*{lemma:grad_map_linearization}}
        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms: 
        \begin{align*}
            & \frac{L}{2}\left(
                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= 
            \frac{L}{2}
            \left(
                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
                + 
                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= \frac{L}{2}\left(
                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
                \Vert^2
            \right), 
        \end{align*}
        therefore it transforms into 
        \begin{align*}
            y_{t + 1} &=\argmin_{x} \left\lbrace
                \frac{L}{2}\left\Vert 
                    x - (y_t - L^{-1}\mathcal G_L(y_t))
                \right\Vert^2
                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &=
            \frac{
                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
            }{L + \eta_{t + 1}^{-1}}.
        \end{align*}
        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, then the above expression simplifies to 
        $$
            y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
        $$
    \end{proof}
    \begin{remark}
        $y_{t + 1}$ is the minimizer of a simple quadratic. 
        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
    \end{remark}

\section{Generic Lyapunov analysis for accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
    \par
    The Lypunov function in 
    \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}}
    is identical to Ahn and Sra 
    \cite[section 4.2]{ahn_understanding_2022}, 
    except for the involvement of the gradient mapping. 
    We adapated it into the context of proximal gradient by 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
    \par
    We present the convergence rate by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
    to assist the proof of  
    \hyperref[thm:generic_ag_convergence]
    {Theorem \ref*{thm:generic_ag_convergence}} 
    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
    \par
    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.

    \begin{lemma}[Lyapunov inequality]
    \label{lemma:nsmooth_agg_lyapunov_upper_bound}\;\\
        Fix any $\bar x, x, z',\tilde\eta > 0$, define
        \begin{align*}
            \phi(u) &:= \tilde\eta
            \left(
                h( \mathcal T_L\bar x) + \langle \mathcal G_L\bar x, u - \bar x\rangle
                + \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2 
            \right), 
            \\
            x^+ &:= 
            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x,
            \\
            \Upsilon_{1}  &:= 
            \tilde \eta(h(\mathcal T_L \bar x) - h(x_*))
            + 
            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2), 
            \\
            \Upsilon_2 &:= 
            h(\mathcal T_L \bar x) - h(z'). 
        \end{align*}
        with $x_*$ being the minimizer of $h$, it has 
        \begin{align*}
            \Upsilon_1 &\le 
            - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
            + 
            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
            - 
            \frac{1}{2}\Vert x^+ - x\Vert^2, 
            \\
            \Upsilon_2 &\le 
            \langle \mathcal G_L\bar x, \mathcal T_L \bar x - z'\rangle + 
            \frac{L}{2}\Vert \mathcal T_L \bar x - \bar x\Vert^2. 
        \end{align*}
    \end{lemma}
    \begin{observation}
        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, at $\bar x$ by 
        \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.
    \end{observation}
    \begin{proof}
        Observe that we have for all $u$: 
        \begin{align*}
            h(u) &\ge 
            h(\mathcal T_L\bar x) + 
            \langle \mathcal G_L \bar x, u - \bar x\rangle + 
            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2
            \\
            &= 
            h(\mathcal T_L \bar x) + 
            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
            + 
            \langle \mathcal G_L \bar x, \mathcal T_L \bar x - \bar x\rangle
            + 
            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x \Vert^2
            \\
            &= 
            h(\mathcal T_L \bar x) + 
            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
            + 
            \langle 
                L (\bar x - \mathcal T_L \bar x)
                , 
                \mathcal T_L \bar x - \bar x
            \rangle
            + 
            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2
            \\
            &= 
            h(\mathcal T_L \bar x) + 
            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
            - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2. 
        \end{align*}
        By PPM descent inequality
        \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}
        , let $x_*$ be a minimizer, it claims that 
        {\small
        \begin{align*}
            & 
            \phi(x^+) - \phi (x^*) + 
            \frac{1}{2}\left(
                \Vert x^+ - x_*\Vert^2 - 
                \Vert x - x_*\Vert^2
            \right)
            \le 
            - \frac{1}{2}\Vert x^+ - x\Vert^2
            \\
            \implies &
            \tilde 
            \eta 
            \left(   
                h(\mathcal T_L \bar x) + 
                \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
                - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
            \right)
            - \tilde \eta h (x_*)
            +
            \frac{1}{2}\left(
                \Vert x^+ - x_*\Vert^2 - 
                \Vert x - x_*\Vert^2
            \right)
            \\
            &\le 
            - \frac{1}{2}\Vert x^+ - x\Vert^2
            \\
            \iff &
            \tilde \eta (h(\mathcal T_L\bar x) - h(x_*))  
            + 
            \frac{1}{2}\left(
                \Vert x^+ - x_*\Vert^2 - 
                \Vert x - x_*\Vert^2
            \right)
            \\
            & \le 
            - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
            + 
            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
            - 
            \frac{1}{2}\Vert x^+ - x\Vert^2. 
        \end{align*}
        }
        Next, for all $z, z'$, it would have by smoothness of $f$: 
        \begin{align*}
            f(z) - f(z') &= 
            f(z) - f(\bar x) + f(\bar x) - f(z')
            \\
            &\le 
            \langle 
                \nabla f(\bar x), z - \bar x
            \rangle + 
            \frac{L}{2}\Vert z - \bar x\Vert^2 
            + 
            \langle 
                \nabla f(\bar x), 
                \bar x - z'
            \rangle
            \\
            &= 
            \langle \nabla f(\bar x), z - z'\rangle
            + 
            \frac{L}{2}\Vert z - \bar x\Vert^2. 
        \end{align*}
        The convexity of $g$ yields for all $v \in \partial g(z)$: 
        \begin{align*}
            g(z) + 
            \langle 
                v, z' - z
            \rangle 
            &\le g(z')
            \\
            g(z) - g(z') 
            &\le 
            \langle v, z - z'\rangle. 
        \end{align*}
        Adding them yield 
        \begin{align*}
            h(z) - h(z') &\le 
            \langle \nabla f(\bar x) +v, z - z'\rangle + 
            \frac{L}{2}\Vert z - \bar x\Vert^2. 
        \end{align*}
        Setting $z = \mathcal T_L \bar x$, use 
        \hyperref[lemma:grad-map-approx-subgrad]
        {Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
        there exists $v \in \partial g (\mathcal T_L(\bar x))$ such that $\mathcal G_L(\bar x) = \nabla f(z) + v$, hence the theorem is proved. 
    \end{proof}
    \begin{remark}\label{remark:upsilon-upperbound-for-iterates}
        Let $y_t, x_t$ be given by
        \hyperref[def:ag_prox_grad_generic]
        {Definition \ref*{def:ag_prox_grad_generic}}.
        Set $\bar x = y_t, x = x_t$, then 
        \begin{align*}
            x^+ &= x_t - \mathcal G_L y_t = x_{t + 1},
            \\
            z_{t + 1} &= \mathcal T_L y_t = \mathcal T_L \bar x.
        \end{align*}
        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, we define the quantities: 
        \begin{align*}
            \Upsilon_{1, t + 1}^{\text{AG}}
            &:= 
            \tilde \eta_{t + 1}(h(z_{t + 1}) - h(x_*))
            + 
            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2),
            \\
            \Upsilon_{2, t + 1}^{\text{AG}}
            &:= 
            h(z_{t + 1}) - h(z_t). 
        \end{align*}
        Then it as inequalities: 
        \begin{align*}
            \Upsilon_{1, t + 1}^{\text{AG}}
            &\le 
            - \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle
            + 
            \frac{\tilde \eta_{t + 1}L}{2}
            \Vert  
                y_t - z_{t + 1}
            \Vert^2
            - 
            \frac{1}{2}
            \Vert x_{t + 1} - x_t\Vert^2,  
            \\ 
            \Upsilon_{2, t + 1}^{\text{AG}}
            &\le 
            \langle \mathcal G_L \bar x, z_{t + 1} - z_t \rangle + 
            \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2.
        \end{align*}
        This is useful for the convergence proof of the algorithm. 
    \end{remark}

>>>>

\title{
    {
        \fontfamily{ptm}\selectfont 
        A Title Here: A Sub Title Here
    }
    }

@@

\begin{abstract} 
    \noindent
    Abstract example citation \cite{bezanson_julia_2017}.

@@

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method.

\section{Introduction}

    \subsection{Contributions}

\section{Preliminaries}\label{sec:preliminaries}
